Capsule Based Aspect Extraction

### 2020-05-29 paper/main.tex
added paper introduction

\section{Introduction}
Aspect extraction is an important and challenging task in aspect-based sentiment analysis. For example, in the sentence "The beef was tender and melted in my mouth", the aspect term is "beef". Two sub-tasks are performed in aspects extraction: (1) extracting all aspects terms(e.g., "beef") from a review corpus, (2) clustering aspect terms with similar meaning into categories where each category represents a single aspect(e.g., cluster "beef", "pork", "pasta", and "tomato" into one aspect food) \cite{He2018ABAE}. in 2017 year, Unsupervised Aspect Extraction \cite{He2018ABAE} have become the dominant unsupervised approach for aspect extraction. In that work neural word embeddings map words with the same context to nearby points in the embedding space \cite{Mikolov2013W2V}. Then attention mechanism \cite{Bahdanau2015NMT} filter the word embeddings within a sentence and filtered words use to construct aspect embeddings. The training process for aspect embeddings is analogous to autoencoders, where dimension reduction use to extract the common factors among embedded sentences and reconstruct each sentence through a linear combination of aspect embeddings. The attention mechanism deemphasizes words that are not part of any aspects, allowing the model to focus on aspect words. That model call \textit{Attention-based Aspect Extraction} (ABAE).

First of all, you will need to write the whole report in English, with a few exceptions mentioned below.
This section is devoted to a problem motivation. You should answer the question of why the problem you were working on is important. Also, you should describe what is unique in your approach to this problem, what are the differences to other approaches.
\subsection{Team}
Please list your team members and describe their responsibilities. Example:

\textbf{Valentin Malykh} prepared this document.

>>>>

\section{Introduction}
Aspect extraction is an important and challenging task in aspect-based sentiment analysis. For example, in the sentence "The beef was tender and melted in my mouth", the aspect term is "beef". Two sub-tasks are performed in aspects extraction: (1) extracting all aspects terms(e.g., "beef") from a review corpus, (2) clustering aspect terms with similar meaning into categories where each category represents a single aspect(e.g., cluster "beef", "pork", "pasta", and "tomato" into one aspect food) \cite{He2018ABAE}. in 2017 year, Unsupervised Aspect Extraction \cite{He2018ABAE} have become the dominant unsupervised approach for aspect extraction. In that work neural word embeddings map words with the same context to nearby points in the embedding space \cite{Mikolov2013W2V}. Then attention mechanism \cite{Bahdanau2015NMT} filter the word embeddings within a sentence and filtered words use to construct aspect embeddings. The training process for aspect embeddings is analogous to autoencoders, where dimension reduction use to extract the common factors among embedded sentences and reconstruct each sentence through a linear combination of aspect embeddings. The attention mechanism deemphasizes words that are not part of any aspects, allowing the model to focus on aspect words. That model call \textit{Attention-based Aspect Extraction} (ABAE). In the same year "Google brain" suggested approach called \textit{Dynamic Routing Between Capsules} \cite{Hinton2017DRBC}. A capsule is a group of neurons whose activity vector represents the instantiation parameters of a specific type of entity such as an object or an object part. The length of the activity vector use to represent the probability that the entity exists and its orientation use to represent the instantiation parameters. Active capsules at one level make predictions, via transformation matrices, for the instantiation parameters of higher-level capsules. When multiple predictions agree, a higher level capsule becomes active. To best performance use iterative routing-by-agreement mechanism: A lower-level capsule prefers to send its output to higher level capsules whose activity vectors have a big scalar product with the prediction coming from the lower-level capsule \cite{Hinton2017DRBC}. In this work i implement ABAE model using pytorch, then change attention mechanism to capsule network and evaluate this models on Citysearch corpus used by previous works\cite{Ganu2009BeyondTheStars}\cite{Brody2010UAS}\cite{Zhao2010JMA}\cite{He2018ABAE}.
